%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
% Version 1.0 (28/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute
% http://www.rpi.edu/dept/arc/training/latex/resumes/
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------

\begin{letter}{}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

\signature{Robert Willison} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Sir of Madam}

\begin{center}
2017 Graduate GPU Compute/Compiler Software Engineer
\end{center}

As you will see from my enclosed CV, I am due to graduate from the University of Bath
this summer with an honours degree in Computer Science. During my last semester I took
a course in advanced compilers which allowed me implement my own compiler for a subset of
C to MIPS assembler, I enjoyed the challenges involved and understanding how to overcome them.
This has led me to search for a role which will allow me to apply and build on these skills. hence my application to
Imagination Technologies.

My course has offered me the opportunity to take a 12 month work placement which I
chose to do with a Bath based company specialising in web based tools for health care. My
role was as a PHP engineer as part of one of their scrum teams. This provided me with
experience of working on a variety of projects and tasks in a team environment. I also
regularly participated in, and occasionally led, meetings with other development teams and
customers.

I would be pleased to supply further information, and I look forward to hearing from you.

\closing{Sincerely yours,}

\end{letter}

\end{document}