\documentclass{letter}
\usepackage{hyperref}
\usepackage[margin=1.0in]{geometry}
\signature{Rob Willison}
\address{4 Cynthia Road \\ Bath \\ BA2 3QH}
\begin{document}

\begin{letter}{}
\vspace*{-10\baselineskip}
\fontsize{12pt}{14pt}\selectfont
\opening{Dear Sir or Madam}

\begin{center}
Graduate Software Developer Role
\end{center}

As you will see from my enclosed CV, I am due to graduate from the University of Bath this
summer with an honours degree in Computer Science.
My course has allowed me to become familiar with the C programming language using it during my final year
for compiler implementation and distributed computing using the OpenMPI library. This has led me
to search for a role which will allow me to apply and build on these skills, and also harness
my interest in engineering, having studied this subject to AS level. Hence my application
to Dyson.

My course has offered me the opportunity to take a 12 month work placement which I chose to do
with a Bath based company specialising in web based tools for health care. My role was
as a PHP engineer as part of one of their scrum teams. This provided me with experience of working on a variety of
projects and tasks in a team environment. I also regularly participated in, and occasionally led,
meetings with other development teams and customers.

I am especially interested in working for Dyson as I would like the opportunity to work for
an internationally renowned technology company with an emphasis on embedded software.
Finally, I would greatly appreciate being given the opportunity to learn from the best in the field in order to
develop my skills and apply them to real world development projects.

I would be pleased to supply further information, and I look forward to hearing from you.
\\~\\
Yours faithfully
\\~\\
Rob Willison

\end{letter}

\end{document}