\documentclass{letter}
\usepackage{hyperref}
\usepackage[margin=1.0in]{geometry}
\signature{Rob Willison}
\address{4 Cynthia Road \\ Bath \\ BA2 3QH}
\begin{document}

\begin{letter}{}
\vspace*{-10\baselineskip}
\fontsize{12pt}{14pt}\selectfont
\opening{Dear Sir or Madam}

As you will see from my enclosed CV, I am due to graduate from the University of Bath
this summer with an honours degree in Computer Science. My course has given me lots of
opportunities in order to explore the fields of machine learning, computer vision and computer graphics
also the opportunity to use many languages including C, Python and Java. For my final
year project I am working with CiteAb, a Bath based start up, on a project which uses
NLP and machine learning techniques, such a Hidden Markov Models, in order to identify
institution names from research papers. This is to be used to help rank the results
returned from there antibody search engine. I am also currently studying a module in computer vision,
this involves creating a face recognition and classification system using
various detection and classification techniques in MATLAB. From
these I have been able to apply and develop my skills in these areas and would like the
opportunity to to continue to do this as a graduate, hence my application to Five AI.

My course has offered me the opportunity to take a 12 month work placement which I chose to do
with a Bath based company specialising in web based tools for health care. My role was
as a PHP engineer as part of one of their scrum teams. This provided me with experience of working on a variety of
projects and tasks in a team environment. I also regularly participated in, and occasionally led,
meetings with other development teams and customers.

I am especially interested in working for Five Ai as I would like the opportunity to work
with a company who are developing autonomous vehicles, I believe this is soon going to
become one of the biggest technological advances in a long time and I wish to be involved
in overcoming the many challenges it involves. Finally, I would greatly appreciate being given the opportunity to learn from the best in the field in order to
develop my skills and apply them to real world development projects.

I would be pleased to supply further information, and I look forward to hearing from you.
\\~\\
Yours faithfully
\\~\\
Rob Willison

\end{letter}

\end{document}