\documentclass{letter}
\usepackage{hyperref}
\usepackage[margin=1.0in]{geometry}
\signature{Rob Willison}
\address{4 Cynthia Road \\ Bath \\ BA2 3QH}
\begin{document}

\begin{letter}{}
\vspace*{-10\baselineskip}
\fontsize{12pt}{14pt}\selectfont
\opening{Dear Sir or Madam}

As you will see from my enclosed CV, I am due to graduate from the University of Bath
this summer with an honours degree in Computer Science. My course has given me lots of
opportunities in order to explore fields such as machine learning, computer networks and graphics
also the opportunity to use many languages like C, Python and Java. However my course rarely touched on the field
of cyber security this has led me to read and learn about it in my own time, enjoying watching the Black Hat
security conference talks. I am now looking for a role which will allow me to explore the
cutting edge of this field, hence my application to PGI Cyber.

My course has offered me the opportunity to take a 12 month work placement which I chose to do
with a Bath based company specialising in web based tools for health care. My role was
as a PHP engineer as part of one of their scrum teams. This provided me with experience of working on a variety of
projects and tasks in a team environment. I also regularly participated in, and occasionally led,
meetings with other development teams and customers.

I am especially interested in working for PGI Cyber as I would like the opportunity to work for
a renowned and accredited company who are at the forefront of cyber security.
Finally, I would greatly appreciate being given the opportunity to learn from the best in the field in order to
develop my skills and apply them to real world development projects.

I would be pleased to supply further information, and I look forward to hearing from you.
\\~\\
Yours faithfully
\\~\\
Rob Willison

\end{letter}

\end{document}